Laplacian envelope

### 2021-11-22 Notes/laplace.tex
use notation macros

In analogy with the case \(s=0\) in \cite{Lahiri2013synapse}, we define
%
\begin{equation}\label{eq:lareacoeffs}
  \begin{aligned}
    {c}_k(s) &= \sum_{ij} \eqm_i \encm_{ij} \prn{\fptbm_{ik}(s)-\fptbm_{jk}(s)}, \\
    {a}_j(s) &= \sum_{k} \encm_{jk} (\etwm_{j}(s) - \etwm_{k}(s)), \\
    \thbm_i(s) &= \sum_j \fptbm_{ij}(0)\, \eqm_j {a}_j(s), \\
  \end{aligned}
    \implies
    \hat{A}(s) 
      % = \sum_k \eqm_k {c}_k(s) \wm_k
      = \mathbf{c}^\dag(s) \w
      = \eq \mathbf{a}(s).
\end{equation}
%
If we regard the \(\wm_k\) as optimisable parameters (limited to the range \( [-1,1] \) wlg.),s the optimal choice is clearly \( \wm_k = \sgn(c_k) \).

@@

The area under the SNR curve is:
%
\begin{equation}\label{eq:areadef}
  \intd[_0^\infty]{t} \snr(t) = \lim_{\tau\to\infty} \tau \snrb(\tau) 
      = A(0) = \frac{\sqrt{N}}{r} \CA = \sqrt{N} \sum_a \CI_a \tau_a.
\end{equation}
%
To maximise this quantity, consider the Lagrangian
%
\begin{equation}\label{eq:arealagrangian}
\begin{aligned}
  \CL =&\, \sum_{ij} \eqm_i \encm_{ij} (\etwm_i(0) - \etwm_j(0))
        +\sum_{\nu i j} \prn{ \kktm^\nu_{ij} \MMdm^\nu_{ij} }
        &+ \lambda \prn{ \Delta p - \sum_i \eqm_i \wm_i },
\end{aligned}
\end{equation}
%
where \(\Delta p\) is the constant value we are holding \(\eq\w\) at.
The Karush-Kuhn-Tucker necessary conditions for a maximum are
%
\begin{equation}\label{eq:KTarea}
  \pdiff{\CL}{\MMdm^\nu_{ij}} = 0, \quad
  \kktm^\nu_{ij} \geq 0, \quad
  \pdiff{\CL}{\kktm^\nu_{ij}} \geq 0, \quad
  \kktm^\nu_{ij}\pdiff{\CL}{\kktm^\nu_{ij}} = 0, \quad
  \pdiff{\CL}{\lambda} = 0.
\end{equation}
%
From \cref{eq:lAdiff}, the derivatives for \(m \neq n\) are
%
\begin{equation}\label{eq:areaderivs}
\begin{aligned}
  \pdiff{\CL}{\MMdm^\nu_{mn}} = & \,
    r f^\nu \eqm_m \prn{ \brk{\thbm_m(0) - \thbm_n(0)}
     + \prn{c_m(0) + (-1)^\nu} \brk{\etwm_m(0) - \etwm_n(0)} } \\
     &+ \kktm^\nu_{mn} -  \kktm^\nu_{mm}
     + \lambda r f^\nu \eqm_m (\etwm_{m}(0)-\etwm_{n}(0)) 
    = 0.
\end{aligned}
\end{equation}
%
See \cref{eq:lareacoeffs} for the definitions of these quantities.

@@

The \(i\)'th row of this equation reads
%
\begin{equation}\label{eq:detarow}
  \frac{\delta\eta_{i+1}+\delta\eta_{i-1}}{2} - (s+1)\delta\eta_i = 0,
\end{equation}
%
with the following exceptions
%
\begin{equation}\label{eq:detabnduni}
\begin{aligned}
  \frac{\delta\eta_2}{2} - \prn{s+\frac{1}{2}}\delta\eta_1 &= 0, \\
  \frac{\delta\eta_{m+1}+\delta\eta_{m-1}}{2} - (s+1)\delta\eta_{m} &= \frac{1}{s},\\
  \frac{\delta\eta_{m+2}+\delta\eta_{m}}{2} - (s+1)\delta\eta_{m+1} &= -\frac{1}{s},\\
  \frac{\delta\eta_{2m-1}}{2} - \prn{s+\frac{1}{2}}\delta\eta_{2m} &= 0.
\end{aligned}
\end{equation}
%
These equations are invariant under \(\delta\eta_{2m+1-i} \to -\delta\eta_i\), so these two must be equal (up to a constant that we can drop).
Then we have
%
\begin{equation}\label{eq:detahalf}
\begin{aligned}
  \frac{\delta\eta_{i+1}+\delta\eta_{i-1}}{2} - (s+1)\delta\eta_i &= 0,
  \quad\text{for}\quad 1<i<m, \\
  \frac{\delta\eta_2}{2} - \prn{s+\frac{1}{2}}\delta\eta_1 &= 0, \\
  \frac{\delta\eta_{m-1}}{2} - \prn{s+\frac{3}{2}}\delta\eta_{m} &= \frac{1}{s}.
\end{aligned}
\end{equation}
%

The first of these equations is solved by
%
\begin{equation}\label{eq:detagensol}
  \delta\eta_i = B\e^{\beta(i-1)} + C\e^{\beta(1-i)},
  \qquad\text{where}\qquad
  s = S(\beta) \equiv 2 \sinh^2 \prn{\frac{\beta}{2}}
    = \cosh (\beta) - 1,
\end{equation}
%
with \(B\) and \(C\) determined by the boundary conditions provided by the last two equations of \eqref{eq:detahalf}:
%
\begin{equation}\label{eq:unicoeffs}
  B = -\frac{1}{s(1 + \e^{-\beta}) \cosh \prn{m \beta}},
  \qquad
  C = -\frac{1}{s(\e^{\beta} + 1) \cosh \prn{m \beta}}.
\end{equation}
%
This can be used to compute the Laplace transform
%
\begin{equation}\label{eq:unilaplace}
  A(s) = \frac{\etwm_1(s)}{m}
   = \frac{1}{m}\prn{\frac{1}{s}+B+C}
   = \frac{2\sinh^2\prn{\frac{m \beta}{2}}}{m s \cosh\prn{m \beta}}
   = \frac{2 S\prn{m \beta}}{M s \prn{S\prn{m \beta} + 1}}.
\end{equation}
%

@@

The \(\etwm_i(s)\) take the same general form \eqref{eq:detagensol} except for \(i=1\), and with different coefficients due to the different boundary conditions
%
\begin{equation}\label{eq:detabndshorten}
\begin{aligned}
  \frac{\delta\eta_2}{2} - \prn{s+\frac{1}{2}}\delta\eta_1 &= 0, \\
  \frac{\delta\eta_3 + (1-\varepsilon)\delta\eta_1}{2} - \prn{s+\frac{2-\varepsilon}{2}}\delta\eta_2 &= 0, \\
  \frac{\delta\eta_{m-1}}{2} - \prn{s+\frac{3}{2}}\delta\eta_{m} &= \frac{1}{s}.
\end{aligned}
\end{equation}
%
These are solved by
%
%
\begin{equation}\label{eq:shortensol}
\begin{aligned}
  \delta\eta_i &= B\e^{(i-2)\beta} + C\e^{(2-i)\beta} \qquad
        \text{for} \quad 2 \leq i \leq m, \\
  \delta\eta_1 &= \frac{1}
         {[(1-\varepsilon)\cosh(m\beta) + \varepsilon(2s+1)\cosh((m-1)\beta)]s}, \\
  B &= - \frac{(2s+1) \e^{\beta/2} + (1-\varepsilon) \tanh(\beta/2)}
         {s [(1-\varepsilon)\cosh(m\beta) + \varepsilon(2s+1)\cosh((m-1)\beta)]}, \\
  C &= - \frac{((2s+1) \e^{-\beta/2} - (1-\varepsilon) \tanh(\beta/2)}
         {s [(1-\varepsilon)\cosh(m\beta) + \varepsilon(2s+1)\cosh((m-1)\beta)]}, \\
\end{aligned}
\end{equation}
%
Which gives the following Laplace transform
%
\begin{equation}\label{eq:shortenlaplace}
  \hat{A}(s) = \frac{(1-\varepsilon) S(m\beta) + \varepsilon(2s+1) S((m-1)\beta)}
          { s [m-\varepsilon]
            [(1-\varepsilon)[S(m\beta) + 1] + \varepsilon(2s+1)[S((m-1)\beta) + 1]] }.
\end{equation}
%
This interpolates between \eqref{eq:unilaplace} at \(\varepsilon=0\) and the same expression for \(m-1\) at \(\varepsilon=1\).

@@

The \(\etwm_i(s)\) take the same general form \eqref{eq:detagensol}, but with different coefficients due to the different boundary conditions
%
\begin{equation}\label{eq:detabndsticky}
\begin{aligned}
  \frac{1 - \varepsilon}{2} \delta \eta_2 
    - \prn{s+\frac{1-\varepsilon}{2}} \delta \eta_1 
    &= 0, \\
  \frac{\delta \eta_{m-1}}{2} 
    - \prn{s+\frac{3}{2}} \delta \eta_{m} 
    &= \frac{1}{s}.
\end{aligned}
\end{equation}
%
These are solved by
%
\begin{equation}\label{eq:stickycoeffs}
\begin{aligned}
  B &= -\frac{\e^{\beta} - \varepsilon}
      {s [\e^{\beta} + 1] [\cosh(m\beta) - \varepsilon \cosh((m-1)\beta)]}, \\
  C &= -\frac{1 - \varepsilon\e^{\beta}}
      {s [\e^{\beta} + 1] [\cosh(m\beta) - \varepsilon \cosh((m-1)\beta)]},
\end{aligned}
\end{equation}
%
which leads to the Laplace transform
%
\begin{equation}\label{eq:stickylaplace}
  \hat{A}(s) = \frac{(1-\varepsilon)}{[m-(m-1)\varepsilon]s} \,
      \brk{\frac{S(m\beta) - \varepsilon S((m-1)\beta)}
      {S(m\beta) - \varepsilon S((m-1)\beta) + 1 - \varepsilon}}.
\end{equation}
%

>>>>

In analogy with the case \(s=0\) in \cite{Lahiri2013synapse}, we define
%
\begin{equation}\label{eq:lareacoeffs}
  \begin{aligned}
    {c}_k(s) &= \sum_{ij} \eqm_i \encm_{ij} \prn{\fptbm_{ik}(s)-\fptbm_{jk}(s)}, \\
    {a}_j(s) &= \sum_{k} \encm_{jk} (\etwm_{j}(s) - \etwm_{k}(s)), \\
    \thbm_i(s) &= \sum_j \fptbm_{ij}(0)\, \eqm_j {a}_j(s), \\
  \end{aligned}
    \implies
    \hat{A}(s) 
      % = \sum_k \eqm_k {c}_k(s) \wm_k
      = \mathbf{c}^\dag(s) \w
      = \eq \mathbf{a}(s).
\end{equation}
%
If we regard the \(\wm_k\) as optimisable parameters (limited to the range \( [-1,1] \) wlg.), the optimal choice is clearly \( \wm_k = \sgn(c_k) \).

@@

The area under the SNR curve is:
%
\begin{equation}\label{eq:areadef}
  \intd[_0^\infty]{t} \snr(t) = \lim_{\tau\to\infty} \tau \snrb(\tau) 
      = A(0) = \frac{\sqrt{N}}{r} \CA = \sqrt{N} \sum_a \CI_a \tau_a.
\end{equation}
%
To maximise this quantity, consider the Lagrangian
%
\begin{equation}\label{eq:arealagrangian}
\begin{aligned}
  \CL =&\, \sum_{ij} \eqm_i \encm_{ij} (\etwm_i(0) - \etwm_j(0))
        +\sum_{\nu i j} \prn{ \kktm^\nu_{ij} \MMdm^\nu_{ij} }
        &+ \lambda \prn{ \Delta p - \sum_i \eqm_i \wm_i },
\end{aligned}
\end{equation}
%
where \(\Delta p\) is the constant value at which we are holding \(\eq\w\).
The Karush-Kuhn-Tucker necessary conditions for a maximum are
%
\begin{equation}\label{eq:KTarea}
  \pdiff{\CL}{\MMdm^\nu_{ij}} = 0, \quad
  \kktm^\nu_{ij} \geq 0, \quad
  \pdiff{\CL}{\kktm^\nu_{ij}} \geq 0, \quad
  \kktm^\nu_{ij}\pdiff{\CL}{\kktm^\nu_{ij}} = 0, \quad
  \pdiff{\CL}{\lambda} = 0.
\end{equation}
%
From \cref{eq:lAdiff}, the derivatives for \(m \neq n\) are
%
\begin{equation}\label{eq:areaderivs}
\begin{aligned}
  \pdiff{\CL}{\MMdm^\nu_{mn}} = & \,
    r f^\nu \eqm_m \prn{ \brk{\thbm_m(0) - \thbm_n(0)}
     + \prn{c_m(0) + (-1)^\nu} \brk{\etwm_m(0) - \etwm_n(0)} } \\
     &+ \kktm^\nu_{mn} -  \kktm^\nu_{mm}
     + \lambda r f^\nu \eqm_m (\etwm_{m}(0)-\etwm_{n}(0)) 
    = 0.
\end{aligned}
\end{equation}
%
See \cref{eq:lareacoeffs} for the definitions of these quantities.

@@

The \(i\)'th row of this equation reads
%
\begin{equation}\label{eq:detarow}
  \frac{\delta\etwm_{i+1}+\delta\etwm_{i-1}}{2} - (s+1)\delta\etwm_i = 0,
\end{equation}
%
with the following exceptions
%
\begin{equation}\label{eq:detabnduni}
\begin{aligned}
  \frac{\delta\etwm_2}{2} - \prn{s+\frac{1}{2}}\delta\etwm_1 &= 0, \\
  \frac{\delta\etwm_{m+1}+\delta\etwm_{m-1}}{2} - (s+1)\delta\etwm_{m} &= \frac{1}{s},\\
  \frac{\delta\etwm_{m+2}+\delta\etwm_{m}}{2} - (s+1)\delta\etwm_{m+1} &= -\frac{1}{s},\\
  \frac{\delta\etwm_{2m-1}}{2} - \prn{s+\frac{1}{2}}\delta\etwm_{2m} &= 0.
\end{aligned}
\end{equation}
%
These equations are invariant under \(\delta\etwm_{2m+1-i} \to -\delta\etwm_i\), so these two must be equal (up to a constant that we can drop).
Then we have
%
\begin{equation}\label{eq:detahalf}
\begin{aligned}
  \frac{\delta\etwm_{i+1}+\delta\etwm_{i-1}}{2} - (s+1)\delta\etwm_i &= 0,
  \quad\text{for}\quad 1<i<m, \\
  \frac{\delta\etwm_2}{2} - \prn{s+\frac{1}{2}}\delta\etwm_1 &= 0, \\
  \frac{\delta\etwm_{m-1}}{2} - \prn{s+\frac{3}{2}}\delta\etwm_{m} &= \frac{1}{s}.
\end{aligned}
\end{equation}
%

The first of these equations is solved by
%
\begin{equation}\label{eq:detagensol}
  \delta\etwm_i = B\e^{\beta(i-1)} + C\e^{\beta(1-i)},
  \qquad\text{where}\qquad
  s = S(\beta) \equiv 2 \sinh^2 \prn{\frac{\beta}{2}}
    = \cosh (\beta) - 1,
\end{equation}
%
with \(B\) and \(C\) determined by the boundary conditions provided by the last two equations of \eqref{eq:detahalf}:
%
\begin{equation}\label{eq:unicoeffs}
  B = -\frac{1}{s(1 + \e^{-\beta}) \cosh \prn{m \beta}},
  \qquad
  C = -\frac{1}{s(\e^{\beta} + 1) \cosh \prn{m \beta}}.
\end{equation}
%
This can be used to compute the Laplace transform
%
\begin{equation}\label{eq:unilaplace}
  A(s) = \frac{\etwm_1(s)}{m}
   = \frac{1}{m}\prn{\frac{1}{s}+B+C}
   = \frac{2\sinh^2\prn{\frac{m \beta}{2}}}{m s \cosh\prn{m \beta}}
   = \frac{2 S\prn{m \beta}}{M s \prn{S\prn{m \beta} + 1}}.
\end{equation}
%

@@

The \(\etwm_i(s)\) take the same general form \eqref{eq:detagensol} except for \(i=1\), and with different coefficients due to the different boundary conditions
%
\begin{equation}\label{eq:detabndshorten}
\begin{aligned}
  \frac{\delta\etwm_2}{2} - \prn{s+\frac{1}{2}}\delta\etwm_1 &= 0, \\
  \frac{\delta\etwm_3 + (1-\varepsilon)\delta\etwm_1}{2} - \prn{s+\frac{2-\varepsilon}{2}}\delta\etwm_2 &= 0, \\
  \frac{\delta\etwm_{m-1}}{2} - \prn{s+\frac{3}{2}}\delta\etwm_{m} &= \frac{1}{s}.
\end{aligned}
\end{equation}
%
These are solved by
%
%
\begin{equation}\label{eq:shortensol}
\begin{aligned}
  \delta\etwm_i &= B\e^{(i-2)\beta} + C\e^{(2-i)\beta} \qquad
        \text{for} \quad 2 \leq i \leq m, \\
  \delta\etwm_1 &= \frac{1}
         {[(1-\varepsilon)\cosh(m\beta) + \varepsilon(2s+1)\cosh((m-1)\beta)]s}, \\
  B &= - \frac{(2s+1) \e^{\beta/2} + (1-\varepsilon) \tanh(\beta/2)}
         {s [(1-\varepsilon)\cosh(m\beta) + \varepsilon(2s+1)\cosh((m-1)\beta)]}, \\
  C &= - \frac{((2s+1) \e^{-\beta/2} - (1-\varepsilon) \tanh(\beta/2)}
         {s [(1-\varepsilon)\cosh(m\beta) + \varepsilon(2s+1)\cosh((m-1)\beta)]}, \\
\end{aligned}
\end{equation}
%
Which gives the following Laplace transform
%
\begin{equation}\label{eq:shortenlaplace}
  \hat{A}(s) = \frac{(1-\varepsilon) S(m\beta) + \varepsilon(2s+1) S((m-1)\beta)}
          { s [m-\varepsilon]
            [(1-\varepsilon)[S(m\beta) + 1] + \varepsilon(2s+1)[S((m-1)\beta) + 1]] }.
\end{equation}
%
This interpolates between \eqref{eq:unilaplace} at \(\varepsilon=0\) and the same expression for \(m-1\) at \(\varepsilon=1\).

@@

The \(\etwm_i(s)\) take the same general form \eqref{eq:detagensol}, but with different coefficients due to the different boundary conditions
%
\begin{equation}\label{eq:detabndsticky}
\begin{aligned}
  \frac{1 - \varepsilon}{2} \delta \etwm_2 
    - \prn{s+\frac{1-\varepsilon}{2}} \delta \etwm_1 
    &= 0, \\
  \frac{\delta \etwm_{m-1}}{2} 
    - \prn{s+\frac{3}{2}} \delta \etwm_{m} 
    &= \frac{1}{s}.
\end{aligned}
\end{equation}
%
These are solved by
%
\begin{equation}\label{eq:stickycoeffs}
\begin{aligned}
  B &= -\frac{\e^{\beta} - \varepsilon}
      {s [\e^{\beta} + 1] [\cosh(m\beta) - \varepsilon \cosh((m-1)\beta)]}, \\
  C &= -\frac{1 - \varepsilon\e^{\beta}}
      {s [\e^{\beta} + 1] [\cosh(m\beta) - \varepsilon \cosh((m-1)\beta)]},
\end{aligned}
\end{equation}
%
which leads to the Laplace transform
%
\begin{equation}\label{eq:stickylaplace}
  \hat{A}(s) = \frac{(1-\varepsilon)}{[m-(m-1)\varepsilon]s} \,
      \brk{\frac{S(m\beta) - \varepsilon S((m-1)\beta)}
      {S(m\beta) - \varepsilon S((m-1)\beta) + 1 - \varepsilon}}.
\end{equation}
%
